TriColorings of Knots

### 2018-04-06 paper/paper.tex

\begin{abstract}
  Tricoloring is a knot invariant that differentiates knots
  based on whether or knot their diagram can be colored in a
  certain way with 3 colors. In this paper we introduce knots
  and define Tricolorability in terms of both knot diagrams
  and the knot group. We then briefly mention extensions
  of the notions of tricolorability to arbitrary $n$-coloring.
\end{abstract}

@@

Second is that we will be considering a subset of knots called tame. A knot
is tame it is ambient isotopic to a piecewise linear knot. An example of
a knot that is not tame is called wild and an example drawing of such can be
seen in figure~\ref{fig:wild}. Wild knots have some more ``pathological''
properties and in order to keep things simple and consistent.

@@

The knot group gives us another invariant of knots. Unfortunately
presentations of groups can be rather difficult to work with.
Thus in order to make the problem more tractable we instead look
at homomorphisms from the knot group to finite groups as these
will be determined by where we send generators. This is
how we will redefine coloring in terms of the knot group~\cite{quickfox}.

>>>>

\begin{abstract}
  Tricoloring is a knot invariant that differentiates knots
  based on whether or knot their diagram can be colored in a
  certain way with 3 colors. In this paper we introduce knots
  and define Tricolorability in terms of both knot diagrams
  and the knot group. We then mention extensions of the notions
  of tricolorability to arbitrary $n$-coloring.
\end{abstract}

@@

Second is that we will be considering a subset of knots called tame. A knot
is tame it is ambient isotopic to a piecewise linear knot. An example of
a knot that is not tame is called wild and an example drawing of such can be
seen in figure~\ref{fig:wild}. Wild knots have some more ``pathological''
properties and to keep things simple and consistent.

@@

The knot group gives us another invariant of knots. Unfortunately
presentations of groups can be rather difficult to work with.
Thus to make the problem more tractable we instead look
at homomorphisms from the knot group to finite groups as these
will be determined by where we send generators. This is
how we will redefine coloring in terms of the knot group~\cite{quickfox}.
